A Survey on Ordered Binary Decision Diagrams

### 2015-09-08 paper.tex
Add BDD and OBDD example figures

\documentclass{vldb}
\usepackage{graphicx}
\usepackage{balance}

\newcommand{\tbr}{\textbf{[TO BE REVISED]}}
\newcommand{\tbd}{\textbf{[TO BE DONE]}}

@@

% title
\title{A Survey on Ordered Binary Decision Diagrams}

% author(s)
\numberofauthors{1}

@@

\textit{Binary decision diagrams} (\textit{BDDs}) have been well studied since
Lee~\cite{LEE59} and especially Akers~\cite{AKERS78} introduced them. BDDs
represent a Boolean function $f$ as an acyclic, directed graph (DAG). Nodes
represent variables and have one incoming and two outgoing edges, each of which
denotes the variable evaluates to 0 (left) or 1 (right), respectively. Whenever
the result of $f$ is fixed, an edge points to one of the constants 0 or 1.
To evaluate $f$ for a given variable assignment, one just follows the path for
the respective variable values. As soon as the path ends up in a constant, i.e. 
0 or 1, this constant value is the result of the variable assignment.
\tbr

>>>>

\documentclass{vldb}

%%% Packages
\usepackage{graphicx}
\usepackage{balance}
\usepackage{tikz}
\usepackage{standalone}
\usepackage{subfigure}

%%% TikZ libraries
\usetikzlibrary{backgrounds, positioning, decorations.pathreplacing, calc, fit}
\usetikzlibrary{shapes}

%%% Macros
\newcommand{\tbr}{\textbf{[TO BE REVISED]}}
\newcommand{\tbd}{\textbf{[TO BE DONE]}}

@@

% Title
\title{A Survey on Ordered Binary Decision Diagrams}

% Author(s)
\numberofauthors{1}

@@

\textit{Binary decision diagrams} (\textit{BDDs}) have been well studied since
Lee~\cite{LEE59} and especially Akers~\cite{AKERS78} introduced them. BDDs
represent a Boolean function $f$ as an acyclic, directed graph (DAG). Nodes
represent variables and have one incoming and two outgoing edges, each of which
denotes the variable evaluates to 0 (left) or 1 (right), respectively. Whenever
the result of $f$ is fixed, an edge points to one of the constant functions
\textbf{0} or \textbf{1}. To evaluate $f$ for a given variable assignment, one
just follows the path for the respective variable values. As soon as the path
ends up in a constant, i.e. \textbf{0} or \textbf{1}, this is the result of the
variable assignment. Akers~\cite{AKERS78} already provided some techniques to
simplify the BDD representation such as combining equivalent nodes.

\begin{figure}[ht]
    \centering
    \subfigure[BDD \newline $f=(A \land B) \lor (B \land C)$.]{
        \includestandalone[height = 3cm]{figs/bdd}
        \label{fig:bdd}
    }
    \hskip1cm
    \subfigure[OBDD \newline $f=(A \land B) \lor (B \land C)$.]{
        \includestandalone[height = 3cm]{figs/obdd}
        \label{fig:obdd}
    }
\end{figure}

\tbr
